cardinalR: Generating interesting high-dimensional data structures

### 2025-05-01 paper-cardinalR.Rmd
Added pyramid projections

>>>>

```{r data-pyrrect, echo=TRUE}
pyrrect <- gen_pyrrect(n = 1000, p = 4)
```

```{r, eval=FALSE}
langevitour::langevitour(pyrrect)
```

```{r pyrrect-proj1}
scaled_data <- scale_data_manual(pyrrect)

pyrrect_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r pyrrect-proj2}

pyrrect_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r pyrrect-proj3}

pyrrect_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.62), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r, label = "fig-pyrrect-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `pyrrect` data."}
#| fig-width: 15
#| fig-height: 5

pyrrect_proj1 + pyrrect_proj2 + pyrrect_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

```{r data-pyrtri, echo=TRUE}
pyrtri <- gen_pyrtri(n = 1000, p = 4)
```

```{r, eval=FALSE}
langevitour::langevitour(pyrtri)
```

```{r pyrtri-proj1}
scaled_data <- scale_data_manual(pyrtri)

pyrtri_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r pyrtri-proj2}

pyrtri_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r pyrtri-proj3}

pyrtri_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.62), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r, label = "fig-pyrtri-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `pyrtri` data."}
#| fig-width: 15
#| fig-height: 5

pyrtri_proj1 + pyrtri_proj2 + pyrtri_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

```{r data-pyrstar, echo=TRUE}
pyrstar <- gen_pyrstar(n = 1000, p = 4)
```

```{r, eval=FALSE}
langevitour::langevitour(pyrstar)
```

```{r pyrstar-proj1}
scaled_data <- scale_data_manual(pyrstar)

pyrstar_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r pyrstar-proj2}

pyrstar_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r pyrstar-proj3}

pyrstar_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.62), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r, label = "fig-pyrstar-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `pyrstar` data."}
#| fig-width: 15
#| fig-height: 5

pyrstar_proj1 + pyrstar_proj2 + pyrstar_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

```{r data-pyrholes, echo=TRUE}
pyrholes <- gen_pyrholes(n = 1000, p = 4)
```

```{r, eval=FALSE}
langevitour::langevitour(pyrholes)
```

```{r pyrholes-proj1}
scaled_data <- scale_data_manual(pyrholes)

pyrholes_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r pyrholes-proj2}

pyrholes_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r pyrholes-proj3}

pyrholes_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.62), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r, label = "fig-pyrholes-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `pyrholes` data."}
#| fig-width: 15
#| fig-height: 5

pyrholes_proj1 + pyrholes_proj2 + pyrholes_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```
